---
title: "Gesture politeness analysis - Korean & Catalan dyads"
author: "Bodo"
date: "29/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Prelims

Load packages:

```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(brms)
library(chron)
```

R and package versions for reporting and reproducibility:

```{r}
R.Version()
packageVersion('tidyverse')
packageVersion('brms')
```

Load data:

```{r, warning = FALSE, message = FALSE}
freq <- read_csv('../data/frequency_size.csv')
path <- read_csv('../data/path_manner_ground_viewpoint.csv')
```

Show:

```{r}
freq
path
```

We can just append the two into a new tibble called 'dyads':

```{r}
dyads <- bind_cols(freq, select(path, TotalEvents:Dual))
```

Create a unique identifier by merging language with ID:

```{r}
dyads <- mutate(dyads,
                ID = str_c(Language, '_', Participant)) %>% 
  select(-Participant) %>% 
  select(ID, Language, Condition, Gender, Total_Freq:Dual)
```

Sort by ID so that polite/informal are next to each other:

```{r}
dyads <- arrange(dyads,
                 ID, Condition)
```

Check one more time:

```{r}
dyads
```

## Add duration data

Load the duration data in:

```{r, message = FALSE, warning = FALSE}
cat_dur <- read_csv('../data/catalan_durations.csv')
kor_dur <- read_csv('../data/korean_durations.csv')
```

Add the label info:

```{r}
cat_dur
kor_dur
```

Create unique identifiers:

```{r}
cat_dur <- mutate(cat_dur,
                  ID = str_c('Catalan_', PPT_ID))
kor_dur <- mutate(kor_dur,
                  ID = str_c('Korean_', PPT_ID))
```

Append:

```{r}
durs <- bind_rows(select(cat_dur, ID, Friend, Prof),
                  select(kor_dur, ID, Friend, Prof))
```

Make this into long format:

```{r}
durs <- pivot_longer(durs, cols = Friend:Prof,
                     names_to = 'Condition',
                     values_to = 'Duration')
```

Transform times to seconds:

```{r}
durs <- mutate(durs,
               Seconds = times(Duration) * 60 * 24)
```

Check:

```{r}
durs
```

Make the labels the same as in the main table:

```{r}
durs <- mutate(durs,
               Condition = ifelse(Condition == 'Prof', 'Superior', Condition))
```

Merge the two:

```{r}
dyads <- durs %>%
  select(-Duration) %>%
  right_join(dyads, by = c('ID', 'Condition'))
```

Check:

```{r}
dyads <- mutate(dyads,
                Seconds = as.vector(Seconds))
```

## Data visualization

Create a dataset with the average rate per speaker:

```{r}
avgs <- dyads %>% 
  mutate(rate = Total_Freq / Seconds) %>% 
  group_by(ID, Condition, Language) %>% 
  summarize(rate_M = mean(rate))
```

Make a variable that codes for whether they go down or not:

```{r}
# Compute differences:

diffs <- avgs %>% group_by(ID) %>% 
  summarize(diff = diff(rate_M)) %>% 
  mutate(trend = ifelse(diff < 0, 'down', 'not down'))

# Add do average data frame:

avgs <- left_join(avgs, diffs)
```

For reporting, trend:

```{r}
avgs %>%
  filter(Condition == 'Superior') %>% 
  ungroup(ID) %>% 
  count(Language, trend)
```

Plot this:

```{r, fig.width = 6, fig.height = 6}
rate_p <- avgs %>% ggplot(aes(x = Condition, y = rate_M,
                       group = ID,
                       fill = Condition)) +
  geom_line(aes(col = trend)) +
  scale_color_manual(values = c('black', 'grey')) +
  geom_point(size = 3, shape = 21,
             alpha = 0.85) +
  scale_fill_manual(values = c("#E69F00", "#0072B2")) +
  xlab('') +
  ylab('Gestures per second') +
  theme_minimal() +
  theme(legend.position = 'none') +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 16,
                                                    b = 0, l = 0),
                                    size = 16, face = 'bold'),
        axis.text.x = element_text(face = 'bold', size = 12),
        strip.text.x = element_text(face = 'bold', size = 16)) +
  facet_wrap(~Language)

# Save:

rate_p
ggsave(plot = rate_p, filename = '../figures/gesture_rate.pdf',
       width = 6, height = 4)
ggsave(plot = rate_p, filename = '../figures/png/gesture_rate.png',
       width = 6, height = 4)
ggsave(plot = rate_p, filename = '../figures/tiff/gesture_rate.tiff',
       width = 6, height = 4)
```





## Settings for Bayesian analysis (same across all)

Settings for parallel processing:

```{r}
options(mc.cores=parallel::detectCores())
```

Weakly informative priors:

```{r}
my_priors <- c(prior('normal(0, 2)', class = 'b'))
```

Control parameters for MCMC sampling:

```{r}
my_controls = list(adapt_delta = 0.999,
                   max_treedepth = 13)
```

Iterations for all chains:

```{r}
my_iter <- 6000
my_warmup <- 4000
```

## Analysis: Gesture frequency

Overall number of gestures per condition:

```{r}
dyads %>% group_by(Condition) %>% 
  summarize(Freq = sum(Total_Freq),
            TotalDur = sum(Seconds)) %>% 
  mutate(Prop = Freq / sum(Freq),
         Prop = round(Prop, 2),
         Percentage = str_c(Prop * 100, '%'),
         Rate = Freq / TotalDur *  60) # per minute
```

Overall number of gestures per condition per language:

```{r}
# Tally by language and condition:

freq_count <- dyads %>% group_by(Language, Condition) %>% 
  summarize(Freq = sum(Total_Freq),
            Dur = sum(Seconds))

# Take sums by language for calculating proportions, and calculate them:

freq_count <- freq_count %>% group_by(Language) %>% 
  summarize(Total = sum(Freq)) %>%
  right_join(freq_count) %>% 
  mutate(Prop = Freq / Total,
         Prop = round(Prop, 2),
         Percentage = str_c(Prop * 100, '%'),
         Rate = Freq / Dur * 60)

# Check:

freq_count
```

Check total frequency by participant:

```{r}
freqs <- dyads %>% select(Language, ID, Condition, Total_Freq) %>% 
  pivot_wider(names_from = Condition, values_from = Total_Freq) %>% 
  mutate(PoliteDiff = Superior - Friend)

# Check:

freqs %>% print(n = Inf)
```

Very consistent picture where Koreans always have less gestures in the superior condition.

Compute for how many this is:

```{r}
freqs <- freqs %>%
  mutate(Category = ifelse(PoliteDiff > 0, 'more polite', PoliteDiff),
         Category = ifelse(Category < 0, 'less polite', Category),
         Category = ifelse(Category == 0, 'same', Category))

# Count:

freqs %>% count(Language, Category)
```

Add the rate information to that:

```{r}
durs <- dyads %>% select(Language, ID, Condition, Seconds) %>% 
  pivot_wider(names_from = Condition, values_from = Seconds)

rates <- left_join(freqs, durs, by = c('Language', 'ID')) %>% 
  rename(Friend_N = Friend.x,
         Superior_N = Superior.x,
         Friend_dur = Friend.y,
         Superior_dur = Superior.y)
```

Calculate the rate difference:

```{r}
rates <- mutate(rates,
                Friend_rate = Friend_N / Friend_dur,
                Superior_rate = Superior_N / Superior_dur,
                PoliteDiff = Superior_rate - Friend_rate)

# Check:

rates %>% select(Language, ID, PoliteDiff) %>% print(n = Inf)
```

Compute for how many the rate lowered / increased:

```{r}
freqs <- freqs %>%
  mutate(Category = ifelse(PoliteDiff > 0, 'more polite', 'less polite'))

# Count:

freqs %>% count(Language, Category)
```

Make a plot of this. First, setup data frame for plotting:

```{r}
freq_avg <- filter(rates,
                   # for Anna Borghi's conference:
                   Language == "Korean") %>% 
  select(ID, Friend_rate, Superior_rate) %>% 
  pivot_longer(Friend_rate:Superior_rate,
               names_to = 'Condition',
               values_to = 'rate') %>% 
  mutate(Condition = ifelse(Condition == 'Friend_rate',
                            'with\nfriend', 'with\nprofessor'))
                   
# Check:

freq_avg
```


For a Poisson model, we'll work with the long format, but we'll have to make language and condition into sum-coded factors to interpret the interaction:

```{r}
# Make into factor:

dyads <- mutate(dyads,
                Language_c = factor(Language),
                Condition_c = factor(Condition))

# Deviation code with Catalan and Friend as reference level (which is the multiplication by -1)

contrasts(dyads$Language_c) <- (contr.sum(2) * -1) / 2
contrasts(dyads$Condition_c) <- (contr.sum(2) * -1) / 2
```

Durations should be log-transformed:

```{r}
dyads <- mutate(dyads,
                LogDur = log(Seconds))
```

Fit Bayesian model:

```{r, warning = FALSE, message = FALSE}
freq_mdl <- brm(Total_Freq ~ Language_c * Condition_c +
                  offset(LogDur) +
                  (1 + Condition_c|ID),
      data = dyads, family = 'negbinomial',
      prior = my_priors,
      control = my_controls,
      seed = 42,
      init = 0, chains = 4, iter = my_iter, warmup = my_warmup)
```

Model summary:

```{r}
summary(freq_mdl)
```

What does the interaction mean? For this the sum-codes need to be checked:

```{r}
contrasts(dyads$Language_c)
contrasts(dyads$Condition_c)
```

Get the posterior probability of the interaction and language effects:

```{r}
posts <- posterior_samples(freq_mdl)
```

Check whether the condition effect is above zero:

```{r}
sum(posts$b_Condition_c1 > 0) / nrow(posts)
```

Check whether the interaction is above zero:

```{r}
sum(posts$`b_Language_c1:Condition_c1` > 0) / nrow(posts)
```

Posterior predictive checks to see whether our model could've predicted the data.

```{r, fig.width = 8, fig.height = 6}
pp_check(freq_mdl, nsamples = 100)
```

Looks good.

## Analysis: Gesture size

Check frequency of vertical and lateral large gestures... which needs to be divided by the total frequency (since the large gestures are a subset of). If we don't calculate proportions, then the result would just be rehashing the total frequency result, as we know that overall gesture rates are lower for superior.

```{r}
vertical <- dyads %>%
  select(Language, ID, Condition, Vertical_Big, Total_Freq) %>% 
  pivot_wider(names_from = Condition,
              values_from = c(Vertical_Big, Total_Freq)) %>%
  mutate(Vertical_Big_Superior = Vertical_Big_Superior / Total_Freq_Superior,
         Vertical_Big_Friend = Vertical_Big_Friend / Total_Freq_Friend,
         PoliteDiff = Vertical_Big_Superior - Vertical_Big_Friend)

lateral <- dyads %>%
  select(Language, ID, Condition, Lateral_Big, Total_Freq) %>% 
  pivot_wider(names_from = Condition,
              values_from = c(Lateral_Big, Total_Freq)) %>%
  mutate(Lateral_Big_Superior = Lateral_Big_Superior / Total_Freq_Superior,
         Lateral_Big_Friend = Lateral_Big_Friend / Total_Freq_Friend,
         PoliteDiff = Lateral_Big_Superior - Lateral_Big_Friend)

sagittal <- dyads %>%
  select(Language, ID, Condition, Sagittal_Big, Total_Freq) %>% 
  pivot_wider(names_from = Condition,
              values_from = c(Sagittal_Big, Total_Freq)) %>%
  mutate(Sagittal_Big_Superior = Sagittal_Big_Superior / Total_Freq_Superior,
         Sagittal_Big_Friend = Sagittal_Big_Friend / Total_Freq_Friend,
         PoliteDiff = Sagittal_Big_Superior - Sagittal_Big_Friend)

# Check:

vertical %>% print(n = Inf)
lateral %>% print(n = Inf)
sagittal %>% print(n = Inf)
```

For plotting, create long format data frames:

```{r}
lateral_avg <- lateral %>% select(Language:Lateral_Big_Superior) %>% 
  pivot_longer(cols = Lateral_Big_Friend:Lateral_Big_Superior,
               names_to = 'Condition',
               values_to = 'Proportion') %>% 
  mutate(Condition = ifelse(Condition == 'Lateral_Big_Friend', 'Friend', 'Superior'))
```

Create the difference labels:

```{r}
# Compute differences:

diffs <- lateral_avg %>% group_by(ID) %>% 
  summarize(diff = diff(Proportion)) %>% 
  mutate(trend = ifelse(diff < 0, 'down', 'not down'))

# Add do average data frame:

lateral_avg <- left_join(lateral_avg, diffs)
```

New ggplots for this:

```{r, fig.width = 4, fig.height = 6}
lateral_p <- lateral_avg %>% ggplot(aes(x = Condition, y = Proportion,
                       group = ID,
                       fill = Condition)) +
  geom_line(aes(col = trend)) +
  scale_color_manual(values = c('black', 'grey')) +
  geom_point(size = 3, shape = 21,
             alpha = 0.85) +
  scale_fill_manual(values = c("#E69F00", "#0072B2")) +
  xlab('') +
  ylab('Proportion of\nlarge gestures (lateral)') +
  theme_minimal() +
  theme(legend.position = 'none') +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 16,
                                                    b = 0, l = 0),
                                    size = 16, face = 'bold'),
        axis.text.x = element_text(face = 'bold', size = 12),
        strip.text.x = element_text(face = 'bold', size = 16)) +
  facet_wrap(~Language)

# Save:

lateral_p
ggsave(plot = lateral_p, filename = '../figures/lateral_gestures.pdf',
       width = 6, height = 4)
ggsave(plot = lateral_p, filename = '../figures/png/lateral_gestures.png',
       width = 6, height = 4)
ggsave(plot = lateral_p, filename = '../figures/tiff/lateral_gestures.tiff',
       width = 6, height = 4)
```

For plotting, create long format data frames:

```{r}
sagittal_avg <- sagittal %>% select(Language:Sagittal_Big_Superior) %>% 
  pivot_longer(cols = Sagittal_Big_Friend:Sagittal_Big_Superior,
               names_to = 'Condition',
               values_to = 'Proportion') %>% 
  mutate(Condition = ifelse(Condition == 'Sagittal_Big_Friend', 'Friend', 'Superior'))
```

Create the difference labels:

```{r}
# Compute differences:

diffs <- sagittal_avg %>% group_by(ID) %>% 
  summarize(diff = diff(Proportion)) %>% 
  mutate(trend = ifelse(diff < 0, 'down', 'not down'))

# Add do average data frame:

sagittal_avg <- left_join(sagittal_avg, diffs)
```

New ggplots for this:

```{r, fig.width = 4, fig.height = 6}
sagittal_p <- sagittal_avg %>% ggplot(aes(x = Condition, y = Proportion,
                       group = ID,
                       fill = Condition)) +
  geom_line(aes(col = trend)) +
  scale_color_manual(values = c('black', 'grey')) +
  geom_point(size = 3, shape = 21,
             alpha = 0.85) +
  scale_fill_manual(values = c("#E69F00", "#0072B2")) +
  xlab('') +
  ylab('Proportion of\nlarge gestures (sagittal)') +
  theme_minimal() +
  theme(legend.position = 'none') +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 16,
                                                    b = 0, l = 0),
                                    size = 16, face = 'bold'),
        axis.text.x = element_text(face = 'bold', size = 12),
        strip.text.x = element_text(face = 'bold', size = 16)) +
  facet_wrap(~Language)

# Save:

sagittal_p
ggsave(plot = sagittal_p, filename = '../figures/sagittal_gestures.pdf',
       width = 6, height = 4)
ggsave(plot = sagittal_p, filename = '../figures/png/sagittal_gestures.png',
       width = 6, height = 4)
ggsave(plot = sagittal_p, filename = '../figures/tiff/sagittal_gestures.tiff',
       width = 6, height = 4)
```


For plotting, create long format data frames:

```{r}
vertical_avg <- vertical %>% select(Language:Vertical_Big_Superior) %>% 
  pivot_longer(cols = Vertical_Big_Friend:Vertical_Big_Superior,
               names_to = 'Condition',
               values_to = 'Proportion') %>% 
  mutate(Condition = ifelse(Condition == 'Vertical_Big_Friend', 'Friend', 'Superior'))
```

Create the difference labels:

```{r}
# Compute differences:

diffs <- vertical_avg %>% group_by(ID) %>% 
  summarize(diff = diff(Proportion)) %>% 
  mutate(trend = ifelse(diff < 0, 'down', 'not down'))

# Add do average data frame:

vertical_avg <- left_join(vertical_avg, diffs)
```

New ggplots for this:

```{r, fig.width = 4, fig.height = 6}
vertical_p <- vertical_avg %>% ggplot(aes(x = Condition, y = Proportion,
                       group = ID,
                       fill = Condition)) +
  geom_line(aes(col = trend)) +
  scale_color_manual(values = c('black', 'grey')) +
  geom_point(size = 3, shape = 21,
             alpha = 0.85) +
  scale_fill_manual(values = c("#E69F00", "#0072B2")) +
  xlab('') +
  ylab('Proportion of\nlarge gestures (vertical)') +
  theme_minimal() +
  theme(legend.position = 'none') +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 16,
                                                    b = 0, l = 0),
                                    size = 16, face = 'bold'),
        axis.text.x = element_text(face = 'bold', size = 12),
        strip.text.x = element_text(face = 'bold', size = 16)) +
  facet_wrap(~Language)

# Save:

vertical_p
ggsave(plot = vertical_p, filename = '../figures/vertical_gestures.pdf',
       width = 6, height = 4)
ggsave(plot = vertical_p, filename = '../figures/png/vertical_gestures.png',
       width = 6, height = 4)
ggsave(plot = vertical_p, filename = '../figures/tiff/vertical_gestures.tiff',
       width = 6, height = 4)
```



Very consistent picture where Koreans always have less gestures in the superior condition. Compute for how many this is:

```{r}
vertical <- vertical %>%
  mutate(Category = ifelse(PoliteDiff > 0, 'more polite', PoliteDiff),
         Category = ifelse(Category < 0, 'less polite', Category),
         Category = ifelse(Category == 0, 'same', Category))
lateral <- lateral %>%
  mutate(Category = ifelse(PoliteDiff > 0, 'more polite', PoliteDiff),
         Category = ifelse(Category < 0, 'less polite', Category),
         Category = ifelse(Category == 0, 'same', Category))
sagittal <- sagittal %>%
  mutate(Category = ifelse(PoliteDiff > 0, 'more polite', PoliteDiff),
         Category = ifelse(Category < 0, 'less polite', Category),
         Category = ifelse(Category == 0, 'same', Category))

# Count:

vertical %>% count(Language, Category)
lateral %>% count(Language, Category)
sagittal %>% count(Language, Category)
```

Create a model for big gestures — can't do this because the denominator isn't right:

```{r}
vertical_mdl <- brm(Vertical_Big | trials(Total_Freq) ~ Language_c * Condition_c +
                 (1 + Condition_c|ID),
               data = dyads, family = binomial,
               prior = my_priors, control = my_controls,
               seed = 42,
               init = 0, chains = 4, iter = my_iter, warmup = my_warmup)

lateral_mdl <- brm(Lateral_Big | trials(Total_Freq) ~ Language_c * Condition_c +
                 (1 + Condition_c|ID),
               data = dyads, family = binomial,
               prior = my_priors, control = my_controls,
               seed = 42,
               init = 0, chains = 4, iter = my_iter, warmup = my_warmup)

sagittal_mdl <- brm(Sagittal_Big | trials(Total_Freq) ~ Language_c * Condition_c +
                 (1 + Condition_c|ID),
               data = dyads, family = binomial,
               prior = my_priors, control = my_controls,
               seed = 42,
               init = 0, chains = 4, iter = my_iter, warmup = my_warmup)
```

Summarize model:

```{r}
summary(vertical_mdl)
summary(lateral_mdl)
summary(sagittal_mdl)
```

Get the posterior probabilities of the big_mdl:

```{r}
vertical_posts <- posterior_samples(vertical_mdl)
lateral_posts <- posterior_samples(lateral_mdl)
sagittal_posts <- posterior_samples(sagittal_mdl)
```

Posterior probability of the condition effect being above 0:

```{r}
sum(vertical_posts$b_Condition_c1 > 0) / nrow(vertical_posts)
sum(lateral_posts$b_Condition_c1 > 0) / nrow(lateral_posts)
sum(sagittal_posts$b_Condition_c1 > 0) / nrow(sagittal_posts)
```

Posterior probability of the interaction effect being above 0:

```{r}
sum(vertical_posts$`b_Language_c1:Condition_c1` > 0) / nrow(vertical_posts)
sum(lateral_posts$`b_Language_c1:Condition_c1` > 0) / nrow(lateral_posts)
sum(sagittal_posts$`b_Language_c1:Condition_c1` > 0) / nrow(sagittal_posts)
```

Posterior predictive checks to see whether our model could've predicted the data, vertical:

```{r, fig.width = 8, fig.height = 6}
pp_check(vertical_mdl, nsamples = 100)
```

Lateral:

```{r, fig.width = 8, fig.height = 6}
pp_check(lateral_mdl, nsamples = 100)
```

Sagittal:

```{r, fig.width = 8, fig.height = 6}
pp_check(sagittal_mdl, nsamples = 100)
```

## Analysis: Use of two-handed gestures

Overall number of gestures per condition:

```{r}
dyads %>% group_by(Condition) %>% 
  summarize(Freq = sum(Both_Hands)) %>% 
  mutate(Prop = Freq / sum(Freq),
         Prop = round(Prop, 2),
         Percentage = str_c(Prop * 100, '%'))
```

Overall number of gestures per condition per language:

```{r}
# Tally by language and condition:

freq_count <- dyads %>% group_by(Language, Condition) %>% 
  summarize(Freq = sum(Both_Hands))

# Tally overall gesture frequency:

freq_totals <- dyads %>% group_by(Language, Condition) %>% 
  summarize(Freq = sum(Total_Freq))

# Take sums by language for calculating proportions, and calculate them:

freq_count <- freq_count %>% group_by(Language) %>% 
  summarize(Total = sum(Freq)) %>%
  right_join(freq_count) %>% 
  mutate(Prop = Freq / Total,
         Prop = round(Prop, 2),
         Percentage = str_c(Prop * 100, '%'))

# Add proportion with total gestures as base rate:

freq_count <- freq_count %>% 
  right_join(freq_totals, by = c('Condition', 'Language')) %>% 
  rename(two_hand_freq = Freq.x,
         total_freq = Freq.y) %>% 
  mutate(prop_new = two_hand_freq / total_freq,
         prop_new = round(prop_new, 2),
         percentage = str_c(prop_new, '%'))

# Check:

freq_count
```


Check frequency of two-handed gestures:

```{r}
both <- dyads %>% select(Language, ID, Condition, Both_Hands, Total_Freq) %>% 
  pivot_wider(names_from = Condition, values_from = c(Both_Hands, Total_Freq)) %>% 
  mutate(Both_Hands_Superior = Both_Hands_Superior / Total_Freq_Superior, 
         Both_Hands_Friend = Both_Hands_Friend / Total_Freq_Friend,
         PoliteDiff = Both_Hands_Superior - Both_Hands_Friend)

# Check:

both %>% print(n = Inf)
```

Very consistent picture where two-handed gestures are used less in the superior context. Compute for how many this is:

```{r}
both <- both %>%
  mutate(Category = ifelse(PoliteDiff > 0, 'more polite', PoliteDiff),
         Category = ifelse(Category < 0, 'less polite', Category),
         Category = ifelse(Category == 0, 'same', Category))

# Count:

both %>% count(Language, Category)
```

Create a data visualization of this:

```{r}
both_avg <- both %>% select(Language:Both_Hands_Superior) %>% 
  pivot_longer(cols = Both_Hands_Friend:Both_Hands_Superior,
               names_to = 'Condition',
               values_to = 'Proportion') %>% 
  mutate(Condition = ifelse(Condition == 'Both_Hands_Friend', 'Friend', 'Superior'))
```

Create the difference labels:

```{r}
# Compute differences:

diffs <- both_avg %>% group_by(ID) %>% 
  summarize(diff = diff(Proportion)) %>% 
  mutate(trend = ifelse(diff < 0, 'down', 'not down'))

# Add do average data frame:

both_avg <- left_join(both_avg, diffs)
```

New ggplots for this:

```{r, fig.width = 4, fig.height = 6}
both_p <- both_avg %>% ggplot(aes(x = Condition, y = Proportion,
                       group = ID,
                       fill = Condition)) +
  geom_line(aes(col = trend)) +
  scale_color_manual(values = c('black', 'grey')) +
  geom_point(size = 3, shape = 21,
             alpha = 0.85) +
  scale_fill_manual(values = c("#E69F00", "#0072B2")) +
  xlab('') +
  ylab('Proportion of\ntwo-handed gestures') +
  theme_minimal() +
  theme(legend.position = 'none') +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 16,
                                                    b = 0, l = 0),
                                    size = 16, face = 'bold'),
        axis.text.x = element_text(face = 'bold', size = 12),
        strip.text.x = element_text(face = 'bold', size = 16)) +
  facet_wrap(~Language)

# Save:

both_p
ggsave(plot = both_p, filename = '../figures/both_gestures.pdf',
       width = 6, height = 4)
ggsave(plot = both_p, filename = '../figures/png/both_gestures.png',
       width = 6, height = 4)
ggsave(plot = both_p, filename = '../figures/tiff/both_gestures.tiff',
       width = 6, height = 4)
```


Create a model for big gestures:

```{r, warning = FALSE, message = FALSE}
both_mdl <- brm(Both_Hands | trials(Total_Freq) ~ Language_c * Condition_c +
                  (1 + Condition_c|ID),
                data = dyads, family = binomial,
                prior = my_priors, control = my_controls,
                seed = 42,
                init = 0, chains = 4, iter = my_iter, warmup = my_warmup)
```

Summarize model:

```{r}
summary(both_mdl)
```

Get the posterior probabilities of the both_mdl:

```{r}
posts <- posterior_samples(both_mdl)
```

Posterior probability of the condition effect being above 0:

```{r}
sum(posts$b_Condition_c1 > 0) / nrow(posts)
```

Posterior probability of the interaction effect being above 0:

```{r}
sum(posts$`b_Language_c1:Condition_c1` > 0) / nrow(posts)
```

Posterior predictive checks to see whether our model could've predicted the data, vertical:

```{r, fig.width = 8, fig.height = 6}
pp_check(both_mdl, nsamples = 100)
```

## Analysis: Use of open-handed gestures

Overall number of gestures per condition:

```{r}
dyads %>% group_by(Condition) %>% 
  summarize(Freq = sum(Shape_Open)) %>% 
  mutate(Prop = Freq / sum(Freq),
         Prop = round(Prop, 2),
         Percentage = str_c(Prop * 100, '%'))
```

Overall number of gestures per condition per language:

```{r}
# Tally by language and condition:

freq_count <- dyads %>% group_by(Language, Condition) %>% 
  summarize(Freq = sum(Shape_Open))

# Tally overall gesture frequency:

freq_totals <- dyads %>% group_by(Language, Condition) %>% 
  summarize(Freq = sum(Total_Freq))

# Take sums by language for calculating proportions, and calculate them:

freq_count <- freq_count %>% group_by(Language) %>% 
  summarize(Total = sum(Freq)) %>%
  right_join(freq_count) %>% 
  mutate(Prop = Freq / Total,
         Prop = round(Prop, 2),
         Percentage = str_c(Prop * 100, '%'))

# Add proportion with total gestures as base rate:

freq_count <- freq_count %>% 
  right_join(freq_totals, by = c('Condition', 'Language')) %>% 
  rename(two_hand_freq = Freq.x,
         total_freq = Freq.y) %>% 
  mutate(prop_new = two_hand_freq / total_freq,
         prop_new = round(prop_new, 2),
         percentage = str_c(prop_new, '%'))

# Check:

freq_count
```

Check frequency of open-handed gestures per speaker:

```{r}
open <- dyads %>% select(Language, ID, Condition, Shape_Open, Total_Freq) %>% 
  pivot_wider(names_from = Condition, values_from = c(Shape_Open, Total_Freq)) %>% 
  mutate(Shape_Open_Superior = Shape_Open_Superior / Total_Freq_Superior, 
         Shape_Open_Friend = Shape_Open_Friend / Total_Freq_Friend,
         PoliteDiff = Shape_Open_Superior - Shape_Open_Friend)

# Check:

open %>% print(n = Inf)
```

Very consistent picture where two-handed gestures are used less in the superior context. Compute for how many this is:

```{r}
open <- open %>%
  mutate(Category = ifelse(PoliteDiff > 0, 'more polite', PoliteDiff),
         Category = ifelse(Category < 0, 'less polite', Category),
         Category = ifelse(Category == 0, 'same', Category))

# Count:

open %>% count(Language, Category)
```

Create a data visualization of this:

```{r}
open_avg <- open %>% select(Language:Shape_Open_Superior) %>% 
  pivot_longer(cols = Shape_Open_Friend:Shape_Open_Superior,
               names_to = 'Condition',
               values_to = 'Proportion') %>% 
  mutate(Condition = ifelse(Condition == 'Shape_Open_Friend', 'Friend', 'Superior'))
```

Create the difference labels:

```{r}
# Compute differences:

diffs <- open_avg %>% group_by(ID) %>% 
  summarize(diff = diff(Proportion)) %>% 
  mutate(trend = ifelse(diff < 0, 'down', 'not down'))

# Add do average data frame:

open_avg <- left_join(open_avg, diffs)
```

New ggplots for this:

```{r, fig.width = 4, fig.height = 6}
open_p <- open_avg %>% ggplot(aes(x = Condition, y = Proportion,
                       group = ID,
                       fill = Condition)) +
  geom_line(aes(col = trend)) +
  scale_color_manual(values = c('black', 'grey')) +
  geom_point(size = 3, shape = 21,
             alpha = 0.85) +
  scale_fill_manual(values = c("#E69F00", "#0072B2")) +
  xlab('') +
  ylab('Proportion of\nopen-handed gestures') +
  theme_minimal() +
  theme(legend.position = 'none') +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 16,
                                                    b = 0, l = 0),
                                    size = 16, face = 'bold'),
        axis.text.x = element_text(face = 'bold', size = 12),
        strip.text.x = element_text(face = 'bold', size = 16)) +
  facet_wrap(~Language)

# Save:

open_p
ggsave(plot = open_p, filename = '../figures/open_handed_gestures.pdf',
       width = 6, height = 4)
ggsave(plot = open_p, filename = '../figures/png/open_handed_gestures.png',
       width = 6, height = 4)
ggsave(plot = open_p, filename = '../figures/tiff/open_handed_gestures.tiff',
       width = 6, height = 4)
```

Create a model for big gestures:

```{r, warning = FALSE, message = FALSE}
open_mdl <- brm(Shape_Open | trials(Total_Freq) ~ Language_c * Condition_c +
                  (1 + Condition_c|ID),
                data = dyads, family = binomial,
                prior = my_priors, control = my_controls,
                seed = 42,
                init = 0, chains = 4, iter = my_iter, warmup = my_warmup)
```

Summarize model:

```{r}
summary(open_mdl)
```

Get the posterior probability of the interaction and language effects for the open mdl:

```{r}
posts <- posterior_samples(open_mdl)
```

Posterior probability of the condition effect being above 0:

```{r}
sum(posts$b_Condition_c1 > 0) / nrow(posts)
```

Posterior probability of the interaction effect being above 0:

```{r}
sum(posts$`b_Language_c1:Condition_c1` > 0) / nrow(posts)
```

Posterior predictive checks to see whether our model could've predicted the data, vertical:

```{r, fig.width = 8, fig.height = 6}
pp_check(open_mdl, nsamples = 100)
```

## Analysis: path, manner, ground

What is the overall number of path, manner, and ground gestures?

```{r}
dyads %>% summarize(Path = sum(Path),
                    Manner = sum(Manner),
                    Ground = sum(Ground))
```


Calculate rate of path/manner/ground encoding per total gestures:

```{r}
dyads <- mutate(dyads,
                Path_p = Path / Total_Freq,
                Manner_p = Manner / Total_Freq,
                Ground_p = Ground / Total_Freq)
```

Calculate path change by speaker and whether it changes based on superiority:

```{r}
path <- dyads %>% select(Language, ID, Condition, Path_p) %>% 
  pivot_wider(names_from = Condition, values_from = Path_p) %>% 
  mutate(PoliteDiff = Superior - Friend)

# Check:

path %>% print(n = Inf)

# Speaker changes overall:

path <- path %>%
  mutate(Category = ifelse(PoliteDiff > 0, 'more polite', PoliteDiff),
         Category = ifelse(Category < 0, 'less polite', Category),
         Category = ifelse(Category == 0, 'same', Category))

# Count:

path %>% count(Language, Category)
```

Same for manner:

```{r}
manner <- dyads %>% select(Language, ID, Condition, Manner_p) %>% 
  pivot_wider(names_from = Condition, values_from = Manner_p) %>% 
  mutate(PoliteDiff = Superior - Friend)

# Check:

manner %>% print(n = Inf)

# Speaker changes overall:

manner <- manner %>%
  mutate(Category = ifelse(PoliteDiff > 0, 'more polite', PoliteDiff),
         Category = ifelse(Category < 0, 'less polite', Category),
         Category = ifelse(Category == 0, 'same', Category))

# Count:

manner %>% count(Language, Category)
```

Same for ground:

```{r}
ground <- dyads %>% select(Language, ID, Condition, Ground_p) %>% 
  pivot_wider(names_from = Condition, values_from = Ground_p) %>% 
  mutate(PoliteDiff = Superior - Friend)

# Check:

ground %>% print(n = Inf)

# Speaker changes overall:

ground <- ground %>%
  mutate(Category = ifelse(PoliteDiff > 0, 'more polite', PoliteDiff),
         Category = ifelse(Category < 0, 'less polite', Category),
         Category = ifelse(Category == 0, 'same', Category))

# Count:

ground %>% count(Language, Category)
```

Data viz for manner:

For plotting, create long format data frames:

```{r}
manner_avg <- manner %>% select(Language:Superior) %>% 
  pivot_longer(cols = Friend:Superior,
               names_to = 'Condition',
               values_to = 'Proportion')
```

Create the difference labels:

```{r}
# Compute differences:

diffs <- manner_avg %>% group_by(ID) %>% 
  summarize(diff = diff(Proportion)) %>% 
  mutate(trend = ifelse(diff < 0, 'down', 'not down'))

# Add do average data frame:

manner_avg <- left_join(manner_avg, diffs)
```

New ggplots for this:

```{r, fig.width = 4, fig.height = 6}
manner_p <- manner_avg %>% ggplot(aes(x = Condition, y = Proportion,
                       group = ID,
                       fill = Condition)) +
  geom_line(aes(col = trend)) +
  scale_color_manual(values = c('black', 'grey')) +
  geom_point(size = 3, shape = 21,
             alpha = 0.85) +
  scale_fill_manual(values = c("#E69F00", "#0072B2")) +
  xlab('') +
  ylab('Proportion of\nmanner gestures') +
  theme_minimal() +
  theme(legend.position = 'none') +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 16,
                                                    b = 0, l = 0),
                                    size = 16, face = 'bold'),
        axis.text.x = element_text(face = 'bold', size = 12),
        strip.text.x = element_text(face = 'bold', size = 16)) +
  facet_wrap(~Language)

# Save:

manner_p
ggsave(plot = manner_p, filename = '../figures/manner_gestures.pdf',
       width = 6, height = 4)
ggsave(plot = manner_p, filename = '../figures/png/manner_gestures.png',
       width = 6, height = 4)
ggsave(plot = manner_p, filename = '../figures/tiff/manner_gestures.tiff',
       width = 6, height = 4)
```

Create models:

```{r, warning = FALSE, message = FALSE}
# Path:

path_mdl <- brm(Path | trials(Total_Freq) ~ Language_c * Condition_c +
                  (1 + Condition_c|ID),
                data = dyads, family = binomial,
                prior = my_priors, control = my_controls,
                seed = 42,
                init = 0, chains = 4, iter = my_iter, warmup = my_warmup)

# Manner:

manner_mdl <- brm(Manner | trials(Total_Freq) ~ Language_c * Condition_c +
                    (1 + Condition_c|ID),
                  data = dyads, family = binomial,
                  prior = my_priors, control = my_controls,
                  seed = 42,
                  init = 0, chains = 4, iter = my_iter, warmup = my_warmup)

# Ground:

ground_mdl <- brm(Ground | trials(Total_Freq) ~ Language_c * Condition_c +
                    (1 + Condition_c|ID),
                  data = dyads, family = binomial,
                  prior = my_priors, control = my_controls,
                  seed = 42,
                  init = 0, chains = 4, iter = my_iter, warmup = my_warmup)
```

Summarize models:

```{r}
summary(path_mdl)
summary(manner_mdl)
summary(ground_mdl)
```

Get the posterior probabilities of each:

```{r}
path_posts <- posterior_samples(path_mdl)
manner_posts <- posterior_samples(manner_mdl)
ground_posts <- posterior_samples(ground_mdl)
```

Posterior probability of the condition effect being above 0:

```{r}
sum(path_posts$b_Condition_c1 > 0) / nrow(path_posts)
sum(manner_posts$b_Condition_c1 > 0) / nrow(manner_posts)
sum(ground_posts$b_Condition_c1 > 0) / nrow(ground_posts)
```

Posterior probability of the interaction effect being above 0:

```{r}
sum(path_posts$`b_Language_c1:Condition_c1` > 0) / nrow(path_posts)
sum(manner_posts$`b_Language_c1:Condition_c1` > 0) / nrow(manner_posts)
sum(ground_posts$`b_Language_c1:Condition_c1` > 0) / nrow(ground_posts)
```

Check the posterior predictive probabilities for each:

```{r, fig.width = 8, fig.height = 6}
pp_check(path_mdl, nsamples = 100)
pp_check(manner_mdl, nsamples = 100)
pp_check(ground_mdl, nsamples = 100)
```

## Analysis: Viewpoint

Overall number of Character, Observer, and Dual:

```{r}
dyads %>% summarize(Character = sum(Character),
                    Observer = sum(Observer),
                    Dual = sum(Observer))
```

Calculate difference in percentage between character and observer viewpoint:

```{r}
dyads <- mutate(dyads,
                Character_p = Character / (Character + Observer),
                Observer_p = Observer / (Character + Observer),
                Viewpoint_diff = Character_p - Observer_p)
```

Do this for speakers to see if this changes for superior versus friend:

```{r}
viewpoint <- dyads %>% select(Language, ID, Condition, Viewpoint_diff) %>% 
  pivot_wider(names_from = Condition, values_from = Viewpoint_diff) %>% 
  mutate(PoliteDiff = Superior - Friend)

# Check:

viewpoint %>% print(n = Inf)
```

Very consistent picture where two-handed gestures are used less in the superior context. Compute for how many this is:

```{r}
viewpoint <- viewpoint %>%
  mutate(Category = ifelse(PoliteDiff > 0, 'more polite', PoliteDiff),
         Category = ifelse(Category < 0, 'less polite', Category),
         Category = ifelse(Category == 0, 'same', Category))

# Count:

viewpoint %>% count(Language, Category)
```

Create a model for viewpoint. We will represent this as a binomial problem since this is a choice of character viewpoint or observer viewpoint. For this we need a "trial" variable (N of the binomial distribution), which will be the sum of observer and character gestures:

```{r}
dyads <- mutate(dyads,
                Trial = Observer + Character)
```

For plotting, create data frame with by-participant data:

```{r}
character_avg <- dyads %>% mutate(Character_prop = Character / Trial) %>% 
  group_by(ID, Language, Condition) %>% 
  summarize(Proportion = mean(Character_prop))
```

Create the difference labels:

```{r}
# Compute differences:

diffs <- character_avg %>% group_by(ID) %>% 
  summarize(diff = diff(Proportion)) %>% 
  mutate(trend = ifelse(diff < 0, 'down', 'not down'))

# Add do average data frame:

character_avg <- left_join(character_avg, diffs)
```

New ggplots for this:

```{r, fig.width = 4, fig.height = 6}
character_p <- character_avg %>% ggplot(aes(x = Condition, y = Proportion,
                       group = ID,
                       fill = Condition)) +
  geom_line(aes(col = trend)) +
  scale_color_manual(values = c('black', 'grey')) +
  geom_point(size = 3, shape = 21,
             alpha = 0.85) +
  scale_fill_manual(values = c("#E69F00", "#0072B2")) +
  xlab('') +
  ylab('Proportion of\ncharacter viewpoint gestures') +
  theme_minimal() +
  theme(legend.position = 'none') +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 16,
                                                    b = 0, l = 0),
                                    size = 16, face = 'bold'),
        axis.text.x = element_text(face = 'bold', size = 12),
        strip.text.x = element_text(face = 'bold', size = 16)) +
  facet_wrap(~Language)

# Save:

character_p
ggsave(plot = character_p, filename = '../figures/character_VP.pdf',
       width = 6, height = 4)
ggsave(plot = character_p, filename = '../figures/png/character_VP.png',
       width = 6, height = 4)
ggsave(plot = character_p, filename = '../figures/tiff/character_VP.tiff',
       width = 6, height = 4)
```


Fit the model:

```{r, warning = FALSE, message = FALSE}
viewpoint_mdl <- brm(Character | trials(Trial) ~ Language_c * Condition_c +
                       (1 + Condition_c|ID),
                     data = dyads, family = binomial,
                     prior = my_priors, control = my_controls,
                     seed = 42,
                     init = 0, chains = 4, iter = my_iter, warmup = my_warmup)
```

Summarize model:

```{r}
summary(viewpoint_mdl)
```

Get the posterior probability of the interaction and language effects for vertical:

```{r}
posts <- posterior_samples(viewpoint_mdl)
```

Posterior probability of the condition effect being above 0:

```{r}
sum(posts$b_Condition_c1 > 0) / nrow(posts)
```

Posterior probability of the interaction effect being above 0:

```{r}
sum(posts$`b_Language_c1:Condition_c1` > 0) / nrow(posts)
```

Posterior predictive checks to see whether our model could've predicted the data, vertical:

```{r, fig.width = 8, fig.height = 6}
pp_check(viewpoint_mdl, nsamples = 100)
```

This completes this analysis.

